Exploring the Pareto front of multi-objective COVID-19 mitigation policies using reinforcement learning

### 2023-03-31 paper/fig/arh_binomial_both.tex
missing data
pieter comments

\begin{tikzpicture}
    \pgfplotsset{
        scale only axis,
        % height=6cm,
        xlabel={total daily new hospitalizations},
        ylabel={total lost contacts},
        width=0.45\textwidth
    }
    \begin{groupplot}[
        group style={
            group size=2 by 1,
            y descriptions at=edge left,
            vertical sep=0pt,
            horizontal sep=0pt,
        },
        legend entries={{$\text{PCN}_{b=2}$}, {$\text{PCN}_{b=3}$}, {$\text{PCN}_{b=4}$}, {$\text{PCN}_{b=5}$}, {$\text{PCN}$}, {Fixed}},
    ]
    % interpolated plot
    \nextgroupplot[draw opacity=1]
    % mean line
    \foreach \b/\c in {2/pc1, 3/pc2, 4/pc3, 5/pc4, {None}/pc5}
    {
        \edef\temp{
            \noexpand\addplot[fill opacity=0.5,\c] table [x=mu_o_1, y=mu_o_5, col sep=comma] {data/cs/arh/binomial/interpolated/budget_\b.csv};
        }
        \temp
    }
    % std fillbetween, has to be after means for legend order
    \foreach \b/\c in {2/pc1, 3/pc2, 4/pc3, 5/pc4, {None}/pc5}
    {
        \edef\temp{
            \noexpand\addplot[name path=upper\b, draw=none] table [x=mu_o_1, y expr=\noexpand\thisrow{mu_o_5}+\noexpand\thisrow{std_o_5}, col sep=comma] {data/cs/arh/binomial/interpolated/budget_\b.csv};
            \noexpand\addplot[name path=lower\b, draw=none] table [x=mu_o_1, y expr=\noexpand\thisrow{mu_o_5}-\noexpand\thisrow{std_o_5}, col sep=comma] {data/cs/arh/binomial/interpolated/budget_\b.csv};
            \noexpand\addplot[\c!15] fill between[of={upper\b} and {lower\b}];
        }
        \temp
    }
    \addplot[only marks,mark=+] table [x=o_0, y=o_1, col sep=comma] {data/cs/cs_fixed.csv};
    % best performing run
    \nextgroupplot[mark size=1pt,draw opacity=1]
    \foreach \b/\c in {2/pc1, 3/pc2, 4/pc3, 5/pc4, {None}/pc5}
    {
        \edef\temp{
            \noexpand\addplot[only marks,mark=o,fill opacity=0.5,\c] table [x=o_1, y=o_5, col sep=comma] {data/cs/arh/binomial/budget_\b.csv};
        }
        \temp
    }
    \addplot[only marks,mark=+] table [x=o_0, y=o_1, col sep=comma] {data/cs/cs_fixed.csv};
    \end{groupplot}
\end{tikzpicture}

>>>>

\begin{tikzpicture}
    \pgfplotsset{
        scale only axis,
        % height=6cm,
        xlabel={total daily new hospitalizations},
        ylabel={total lost contacts},
        width=0.45\textwidth
    }
    \begin{groupplot}[
        group style={
            group size=2 by 1,
            y descriptions at=edge left,
            vertical sep=0pt,
            horizontal sep=0pt,
        },
        legend entries={{$\text{PCN}_{b=2}$}, {$\text{PCN}_{b=3}$}, {$\text{PCN}_{b=4}$}, {$\text{PCN}_{b=5}$}, {$\text{PCN}_{b=\infty}$}, {Fixed}},
    ]
    % interpolated plot
    \nextgroupplot[mark size=1pt,draw opacity=1]
    % mean line
    \foreach \b/\c in {2/pc1, 3/pc2, 4/pc3, 5/pc4, {None}/pc5}
    {
        \edef\temp{
            \noexpand\addplot[fill opacity=0.5,\c] table [x=mu_o_1, y=mu_o_5, col sep=comma] {data/cs/arh/binomial/interpolated/budget_\b.csv};
        }
        \temp
    }
    % std fillbetween, has to be after means for legend order
    \foreach \b/\c in {2/pc1, 3/pc2, 4/pc3, 5/pc4, {None}/pc5}
    {
        \edef\temp{
            \noexpand\addplot[name path=upper\b, draw=none] table [x=mu_o_1, y expr=\noexpand\thisrow{mu_o_5}+\noexpand\thisrow{std_o_5}, col sep=comma] {data/cs/arh/binomial/interpolated/budget_\b.csv};
            \noexpand\addplot[name path=lower\b, draw=none] table [x=mu_o_1, y expr=\noexpand\thisrow{mu_o_5}-\noexpand\thisrow{std_o_5}, col sep=comma] {data/cs/arh/binomial/interpolated/budget_\b.csv};
            \noexpand\addplot[\c!15] fill between[of={upper\b} and {lower\b}];
        }
        \temp
    }
    \addplot[only marks,mark=+] table [x=o_0, y=o_1, col sep=comma] {data/cs/cs_fixed.csv};
    % best performing run
    \nextgroupplot[mark size=1pt,draw opacity=1]
    \foreach \b/\c in {2/pc1, 3/pc2, 4/pc3, 5/pc4, {None}/pc5}
    {
        \edef\temp{
            \noexpand\addplot[only marks,mark=o,fill opacity=0.5,\c] table [x=o_1, y=o_5, col sep=comma] {data/cs/arh/binomial/budget_\b.csv};
        }
        \temp
    }
    \addplot[only marks,mark=+] table [x=o_0, y=o_1, col sep=comma] {data/cs/cs_fixed.csv};
    \end{groupplot}
\end{tikzpicture}
